%-------------------------
% Resume in Latex
% Author : Jake Gutierrez, Sourabh Bajaj, Tobias Pfanzelter
% Based off of: https://github.com/sb2nov/resume (MIT license)
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Tobias Pfandzelter} \\
    \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ +49 172 960 8059 ~ \href{mailto:tobias@pfandzelter.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{tobias@pfandzelter.com}} ~
    \href{https://pfandzelter.com/}{\raisebox{-0.2\height}\faGlobe\ \underline{pfandzelter.com}} \\
    \vspace{5pt}
    Third-year Computer Science PhD candidate in the field of distributed and scalable software systems. Current research interests include edge and fog computing, particularly in the context of novel LEO satellite communication systems.
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technische Universität Berlin}{Sep. 2019 -- present}
      {Computer Science, Doctoral Degree}{Berlin, Germany}
      \resumeSubheading
      {Center for Cultural Studies on Science and Technology in China (CCST)}{Mar. 2020}
      {China Master Label}{Berlin, Germany}
      \resumeSubheading
      {Tongji University Shanghai}{Sep. 2019}
      {``Smart Shanghai'' Summer School}{Shanghai, China}
      \resumeSubheading
      {Technische Universität Berlin}{Oct. 2017 -- Aug. 2019}
      {\begin{tabular}[l]{@{}l@{}}Master of Science in Computer Science\\Distributed Systems and Networks Focus\\Grade 1.0 (equiv. 4.0 GPA)\end{tabular}}{Berlin, Germany}
      \resumeSubheading
      {Technische Universität Berlin}{Oct. 2014 -- Mar. 2018}
      {Bachelor of Science in Computer Science}{Berlin, Germany}
  \resumeSubHeadingListEnd

%
%-----------PUBLICATIONS-----------
\section{Select Peer-Reviewed Publications}
 \begin{itemize}[leftmargin=0.15in]
    \small{
    \item T. Pfandzelter and D. Bermbach, ``Edge (of the Earth) Replication: Optimizing Content Delivery in Large LEO Satellite Communication Networks,'' in \emph{Proceedings of the 2021 IEEE/ACM 21st International Symposium on Cluster, Cloud and Internet Computing (CCGrid)}, Melbourne, Australia, May 2021.
    \item T. Pfandzelter, J. Hasenburg, and D. Bermbach, ``Towards a Computing Platform for the LEO Edge,'' in \emph{Proceedings of ACM EdgeSys ’21: 4th International Workshop on Edge Systems, Analytics and Networking}, Online, United Kingdom, Apr. 2021.
    \item T. Pfandzelter and D. Bermbach, ``tinyFaaS: A Lightweight FaaS Platform for Edge Environments,'' in \emph{Proceedings of the 2020 IEEE International Conference on Fog Computing (ICFC)}, Sydney, Australia, Apr. 2020, pp. 17–24.
    }
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\begin{tabular}[l]{@{}l@{}}Mobile Cloud Computing Research Group,\\Technische Universität Berlin \& Einstein Center Digital Future\end{tabular}}{Sep. 2019 -- present}
      {Research Associate}{Berlin, Germany}
      \resumeItemListStart
        \resumeItem{Responsible for the \emph{FogStore} project, which aims to develop a data management middleware for the edge and cloud.}
        \resumeItem{Extensive development of open-source distributed systems software prototypes in Go and Python.}
        \resumeItem{Authored and published several peer-reviewed research papers, posters, and articles.}
        \resumeItem{Supervising student assistants, student projects, and student theses.}
      \resumeItemListEnd

    \resumeSubheading
      {audibene GmbH}{Mar. 2015 -- Aug. 2019}
      {Systems Administrator}{Berlin, Germany}
      \resumeItemListStart
        \resumeItem{Scaled IT infrastructure for a start up from 200 to more than 1,000 employees globally.}
        \resumeItem{Research, procurement, development, and administration of internal software and tools while working with different teams across the organization.}
        \resumeItem{Agile management of IT projects to meet customer needs in a fast-paced environment.}
        \resumeItem{Development and administration of a hybrid cloud and global enterprise network.}
    \resumeItemListEnd

    \resumeSubheading
      {Coca-Cola Erfrischungsgetränke AG}{Sep. 2014}
      {IT Intern}{Berlin, Germany}
      \resumeItemListStart
        \resumeItem{Learned about IT structures and processes in a large corporation.}
        \resumeItem{Managed my own small project to develop software for internal use.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Go (highly proficient), Python, JavaScript, HTML/CSS (proficient), Java, C\#} \\
     \textbf{Technologies}{: Docker, Linux, Networking, Microservices, TCP/IP, Web \& Internet, AWS, GCP, Microsoft Azure} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%
%-----------LANGUAGES-----------

\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{German}{: Native} \\
     \textbf{English}{: Fluent}} \\
     \textbf{Chinese}{: Basic}} \\
 \end{itemize}
 \vspace{-16pt}

\end{document}
